Energy Injection for Mechanical Systems via Virtual Nonholonomic Constraints

### 2020-02-29 latex/bcc/main.tex
Edit the abstract
This commit edits the abstract for the 2020 BCC to have more interesting
and natural language, and removes some errors while rephrasing certain
sections.

%---------- Bibliography Style ----------%
\usepackage[style=ieee,backend=biber]{biblatex}
\addbibresource{bib.bib}

@@

%----------- Math Packages -----------%
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{amsthm} % allow theorems and definitions as a block

@@

%---------- Content ----------%
When a gymnast hanging on a bar performs a swing-up routine (a so-called ``giant"),
they do not attempt to track a trajectory over time to start doing backflips.
Likewise, a child on a swing does not swing higher by kicking their legs at
specific time intervals; rather, these natural human motions change one's leg
angle based on the current direction and speed of motion. In doing so, the
gymnast will gain enough energy to start rotating on the bar, 
and the child will reach greater heights on their swing.
This type of motion can be adapted to the control of mechanical systems 
using the method of virtual nonholonomic constraints.

A \textit{virtual nonholonomic constraint} (VNHC) is a smooth relation 
\[
    h : T^\star \mathcal{Q} \rightarrow \mathbb{R}^{n-1}
\]
between the \(n\) configuration variables \(q \in \mathcal{Q}\) and conjugate of
momenta \(p\) of a mechanical system with \(n-1\) control inputs.
Enforcing these types of constraints via feedback control provides
time-independent controllers which can inject or remove energy from the system.

This talk will give sufficient conditions under which a VNHC 
can be enforced by feedback control.
Then, using the motivations of the child on the swing and the gymnast,
we apply the theory to create VNHCs for two classical mechanical systems:
the variable-length pendulum and the two-link acrobot.

For the variable-length pendulum we design and enforce a VNHC which achieves a
time-optimal swingup motion, without tracking a time signal. 
Then, we prove that a system constrained by this VNHC will gain energy and start
rotating.

For the acrobot, we design several VNHCs which achieve human-like motion by
observing the leg motions of human gymnasts. We then apply one of these
VNHCs to a real acrobot and, through experiments, demonstrate the
energy-injection properties of the VNHC.

This talk demonstrates the potential of VNHCs in generating realistic,
biologically-inspired motions which can inject energy into a mechanical system
while forgoing any dependence on time in the control architecture.

%---------- Bibliography ----------%
\newpage
\printbibliography
\end{document}
%/========== /Main Document ==========/%

>>>>

%---------- Bibliography Style ----------%
%\usepackage[style=ieee,backend=biber]{biblatex}
%\addbibresource{bib.bib}

@@

%----------- Math Packages -----------%
\usepackage{amsfonts}
\usepackage{mathtools}

@@

%---------- Motivation ----------%
When a gymnast is hanging on a bar, they do not attempt to track a trajectory
over time to perform their swing-up routine (a so-called ``giant");
likewise, a child on a standing swing does not swing higher by standing or
squatting at specific time intervals. 
Rather, these natural human motions involve moving one's legs based on the
current direction and speed of motion. 
In doing so, the gymnast will gain enough energy to start rotating on the bar,
and the child will reach greater heights on their swing. 
This style of realistic, energy-increasing motion can be achieved when
controlling mechanical systems by using the method of virtual nonholonomic
constraints.

%---------- Summary of Ideas ----------%
A \textit{virtual nonholonomic constraint} (VNHC) is a smooth relation 
\[
    h : T^\star \mathcal{Q} \rightarrow \mathbb{R}^{n-1}
\]
between the \(n\) configuration variables \(q \in \mathcal{Q}\) and conjugate of
momenta \(p \in T_q^\star\mathcal{Q}\) of a mechanical system with 
\(n-1\) control inputs.
Enforcing these types of constraints via feedback control provides
time-independent controllers which can inject or remove energy from the system.

%---------- Results ----------%
This talk will give sufficient conditions under which a VNHC can be enforced by
feedback control.
Then, using the motivations of the child on the standing swing and the gymnast
on a bar, we apply the theory to develop energy-injecting VNHCs for two
classical systems: the variable-length pendulum and the two-link acrobot.

For the variable-length pendulum we design and enforce a VNHC which achieves a
time-optimal swingup motion, without tracking a signal over time. 
We then prove that anyone swinging while constrained by this VNHC will gain
enough energy to start rotating completely around the swinging axis.

For the acrobot, we design several VNHCs (modelled from the leg motions of human
gymnasts) which achieve human-like ``giant" motion.
We then apply one of these VNHCs to a real acrobot and, through experiments,
demonstrate the energy-injection properties of the VNHC as the robot kicks its
legs and starts doing backflips on the bar.

%---------- Conclusion ----------%
In summary, this talk introduces the notion of virtual nonholonomic constraints
and demonstrates their potential for generating realistic, biologically-inspired
motions which inject energy into mechanical systems while forgoing any
dependence on time in the control architecture.

%---------- Bibliography ----------%
%\newpage
%\printbibliography
\end{document}
%/========== /Main Document ==========/%
